% BOD

\zchinrsetup{
  reset,
  article = {
    pagination = {none}
  }
}

\newcommand{\ZChinRBackColumnsLeft}{%
  \begin{otherlanguage}{english}\frenchspacing%
  The German--Chinese Jurists' Association and the Sino--German Institute for Legal Studies of the Universities of Göttingen and Nanjing have been publishing the \emph{Zeitschrift für Chinesisches Recht}\,/\,\emph{German Journal of Chinese Law}, formerly the \emph{Newsletter of the German--Chinese Jurists' \mbox{Association}}, quarterly since 1994.
  
  \bigskip

  The journal focuses on contemporary Chinese law and modern Chinese legal history, with a particular emphasis on legal aspects of Chinese economic development and international relations. It seeks to advance the analysis of Chinese law from practical as well as theoretical standpoints.

  \bigskip

  Beginning in 2025, all contributions to the journal will be published open access under the CC BY 4.0 licence. All issues and articles published in the journal since 2004 are available for download at \url{www.ZChinR.org}. Currently, the journal registers over 30.000 article downloads per year.%
  \end{otherlanguage}%
}

\newcommand{\ZChinRBackColumnsRight}{%
  \begin{otherlanguage}{english}\frenchspacing%
  The journal welcomes the submission of articles within its ambit for publication in an upcoming issue. To ensure that the journal's contents are innovative and intellectually stimulating, all submissions are subject to prior editorial review and a subsequent peer review. Manuscripts in English or German for publication in one of the journal's categories (articles, short contributions, documentation, and book reviews) should be submitted electronically, and authors should observe the citation and other submission guidelines, which can be found at \url{www.ZChinR.org}.
  
  \bigskip

  Please address your manuscripts, as well as any inquiries concerning subscription and advertising, to:
  
  \bigskip

  ZChinR, Sino--German Institute for Legal Studies \\
  Nanjing University \\
  No. 22, Hankou Lu \\ 
  210093 Nanjing, PR China

  \bigskip

  E-mail: zchinr@dcjv.org \\ 
  Phone\,/\,Fax: +86 25 8663 7892%
  \end{otherlanguage}%
}

\begin{drawabsolute}[10mm,-10mm]
  
  % \drawrectangle[zchinrblue!10]{20mm,-20mm}{170mm,-257mm}

  \drawrectangle[zchinrblue!33]{-3mm,3mm}{216mm,-143mm}

  \drawcoffin[zchinrblue]{210mm-20mm,-20mm}{100mm}[r][t]{%
    \raggedleft%
    \zchinrlatindisplay%
    \Large\bfseries%
    ISSN: 1613-5768 \\ eISSN: 2366-7125%
  } 
  
  \drawcoffin[zchinrblue]{20mm,-107.5mm}{170mm}[l][t]{%
    \zchinrlatindisplay%
    \fontsize{70}{65}\selectfont%
    ZChinR \char"00B7{} GJCL%
  }

  \drawcoffin[zchinrblue]{20mm,-297mm+145mm}{170mm}[l][t]{%
    \sffamily%
    \Huge%
    Zeitschrift für Chinesisches Recht \\
    German Journal of Chinese Law% 
  }
  
  \drawcoffin[zchinrblue]{20mm,-297mm+115mm}{80mm}[l][t]{%
    \sloppy%
    \sffamily%
    \ZChinRBackColumnsLeft%
  }
  
  \drawcoffin[zchinrblue]{110mm,-297mm+115mm}{80mm}[l][t]{%
    \sloppy%
    \sffamily%
    \ZChinRBackColumnsRight%
  }

\end{drawabsolute}

% EOF